SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-03 docs/questioning.tex
SMasK goes to ISR

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.
Contrary to x{\sc js}, in Noncespaces administrators must set
specific policies in a manner similar to a firewall
configuration language. This brings up questions
concerning the diagnostic performance of the mechanism
since the corresponding testing is insufficient
(see Table~\ref{tab:comp}).

@@

There are different implementations of these approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (locus {\sc z}).
However, this is a simplistic approach that may
lead to many false positives.

The following schemes apply further checks when
they identify that tainted data have reached a sink.
In particular, {\it Xu et al.}~\cite{XBS06}
tracks taint information at the level of bytes in memory.
To distinguish between legitimate and malicious uses
of untrusted data that reach a sink,
they search the data for suspicious symbols by using
regular expressions. {\sc csse}~\cite{PB05} associates
tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application
and other. When tainted data reaches a sink {\sc csse} performs
syntactic checks it based on the aforementioned metadata
(locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
in a similar way. To obtain metadata, it takes advantage
of specific features provided by {\sc php}.
Note that the above schemes detect potential attacks
in locus {\sc z}. This automatically means that they
cannot detect non-persistent JavaScript-driven
{\sc xss} attacks. {\sc wasc}~\cite{NLC07} 
though, can deal with such attacks because it
analyzes {\sc html} responses to check
if there are tainted data that contain scripts (locus {\sc y}).
A recent study showed that there are ways to circumvent
the majority of the above schemes~\cite{NBR14}.
Furthermore, most of them are hard to deploy since
the majority of input vectors, string operations
and output vectors must be instrumented.

{\it Vogt et al.}~\cite{VFJKKV07}
have developed a tainting scheme that follows a different
approach. Contrary to the aforementioned schemes that
operate on the server side, they track taint sensitive
information on the client side (locus {\sc x}).
This is a form of positive taint tracking, where
taint data is considered to be legitimate.
In essence, they detect JavaScript-driven {\sc xss}
attacks by ensuring that a script can send sensitive
user data only to the site from which it came from.
This though, may lead to false alarms.
{\it Stock et al.}~\cite{SLMS14} propose a scheme
that also operates in the browser (locus {\sc x}).
The scheme focuses on the detection of
{\sc dom}-based {\sc xss} attacks.
In such an attack, the malicious payload is
executed as a result of the modification of the
{\sc dom} environment so that the client-side
code runs in an unanticipated manner even if the
{\sc http} response that triggers the injection seems legitimate.
The scheme is different to the previous one because it
marks and observes data that are considered harmful.
Specifically, it employs a taint-enhanced JavaScript
engine that tracks the flow of attacker-controlled data.
To detect potential attacks the scheme utilizes
{\sc html} and JavaScript parsers that can
identify the generation of code coming from
tainted data.

@@

{\it {\sc sm}ask}~\cite{JB07} is a mechanism that detects
both {\sc sql} injection attacks and {\sc xss} attacks.
To do this, it identifies malicious
code by automatically separating user input from legitimate code.
This is done by introducing specific syntactic constructs
that handle server-side languages used for data management
separately.

@@

  \multirow{3}{*}{{\sc isr}}

@@

  \multirow{4}{*}{Hybrid}

>>>>

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.
Contrary to x{\sc js}, in Noncespaces administrators must set
specific policies in a manner similar to a firewall
configuration language. This brings up questions
concerning the diagnostic performance of the mechanism
since the corresponding testing is insufficient
(see Table~\ref{tab:comp}).
{\it {\sc sm}ask}~\cite{JB07} is another framework
that was inspired by {\sc isr}. To detect {\sc xss}
attacks it searches for {\sc html} and JavaScript
keywords within the application's legitimate code.
This is done before the processing of an {\sc http}
request. When it finds one it adds a token to it.
This results to a ``code mask". Then,
before sending the resulting {\sc html} data to the
web user, the framework searches the data for
illegal code by using the same keywords.
Since all legitimate code has been ``masked",
the injected code can be identified.
The pre- and post-processing of the code though,
may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask
did not provide measurements regarding the
computational performance of the tool (see Table~\ref{tab:comp}).

@@

There are different implementations of these approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (locus {\sc z}).
However, this is a simplistic approach that may
lead to many false positives.
The following schemes apply further checks when
they identify that tainted data have reached a sink.
In particular, {\it Xu et al.}~\cite{XBS06}
tracks taint information at the level of bytes in memory.
To distinguish between legitimate and malicious uses
of untrusted data that reach a sink,
they search the data for suspicious symbols by using
regular expressions. {\sc csse}~\cite{PB05} associates
tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application
and other. When tainted data reaches a sink {\sc csse} performs
syntactic checks it based on the aforementioned metadata
(locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
in a similar way. To obtain metadata, it takes advantage
of specific features provided by {\sc php}.
Note that the above schemes detect potential attacks
in locus {\sc z}. This automatically means that they
cannot detect non-persistent JavaScript-driven
{\sc xss} attacks. {\sc wasc}~\cite{NLC07} 
though, can deal with such attacks because it
analyzes {\sc html} responses to check
if there are tainted data that contain scripts (locus {\sc y}).
A recent study showed that there are ways to circumvent
the majority of the above schemes~\cite{NBR14}.
Furthermore, most of them are hard to deploy since
the majority of input vectors, string operations
and output vectors must be instrumented.

{\it Vogt et al.}~\cite{VFJKKV07}
have developed a tainting scheme that follows a different
approach. Contrary to the aforementioned schemes that
operate on the server side, they track taint sensitive
information on the client side (locus {\sc x}).
This is a form of positive taint tracking, where
taint data is considered to be legitimate.
Their scheme detects JavaScript-driven {\sc xss}
attacks by ensuring that a script can send sensitive
user data only to the site from which it came from.
This though, may lead to false alarms.
{\it Stock et al.}~\cite{SLMS14} propose a scheme
that also operates in the browser (locus {\sc x}).
The scheme focuses on the detection of
{\sc dom}-based {\sc xss} attacks.
In such an attack, the malicious payload is
executed as a result of the modification of the
{\sc dom} environment so that the client-side
code runs in an unanticipated manner even if the
{\sc http} response that triggers the injection seems legitimate.
The scheme is different to the previous one because it
marks and observes data that are considered harmful.
Specifically, it employs a taint-enhanced JavaScript
engine that tracks the flow of attacker-controlled data.
To detect potential attacks the scheme utilizes
{\sc html} and JavaScript parsers that can
identify the generation of code coming from
tainted data.

@@

@@

  \multirow{4}{*}{{\sc isr}}

@@

  \multirow{3}{*}{Hybrid}
